Integration of national demographic-disturbance relationships into local caribou population viability projections can reduce uncertainty and inform monitoring decisions

### 2025-01-23 analysis/paper/supplement.Rmd
fix lambdas
MS revisions in progress

resultScenario = "S11"
noBiasResultScenario = "S12"

@@

|$\tilde{lambda}_{t}$|rate|Expected annual population growth.|

@@

|$\bar{lambda}_{t}$|rate|Expected annual population growth.|

@@

We begin by setting random effects to zero, varying the prior standard deviations of the survival intercept (sIntSE is $\beta^S_0$ in Table 2) and recruitment intercept (rIntSE is $\beta^R_0$ in Table 2), and comparing the prior predictive intervals of the Bayesian model to the 95\% predictive intervals from Johnson et al.'s (2020) regression analysis in a case with no anthropogenic disturbance (top row of Fig \@ref(fig:InterceptsAndSlopes)). We set the prior standard deviation intercept parameters (sIntSE = 0.04, rIntSE = 0.25) so that the upper bounds of the Bayesian predictive intervals match the upper bounds of Johnson et al.'s predictive intervals.

@@

```{r figEVPI, fig.cap="The expected value of perfect information (EVPI) varies among anthropogenic disturbance scenarios (see increasing, decreasing and stable scenarios in Figs 1, D.1 and D.5 respectively) and the number of years projected. When disturbance is high EVPI is low, indicating that local sampling will not alter status assessments. Increasing the forecast horizon can either increase or decrease the EVPI as the anthropogenic disturbance trend makes outcomes more or less predictable.", cache=TRUE}
knitr::include_graphics(here::here(paste0("figs/",resultScenario,"/EVPIall.png")))
```

>>>>

resultScenario = "S11"
noBiasResultScenario = "S14"

@@

|$\tilde{\lambda}_{t}$|rate|Expected annual population growth.|

@@

|$\bar{\lambda}_{t}$|rate|Expected annual population growth.|

@@

We begin by setting random effects to zero, varying the prior standard deviations of the survival intercept (sIntSE is $\beta^S_0$ in Table 2) and recruitment intercept (rIntSE is $\beta^R_0$ in Table 2), and comparing the prior predictive intervals of the Bayesian model to the 95\% predictive intervals from Johnson et al.'s (2020) regression analysis in a case with no anthropogenic disturbance (top row of Fig \@ref(fig:InterceptsAndSlopes)). We set the prior standard deviation intercept parameters (sIntSE = 0.06, rIntSE = 0.35) so that the lower bounds of the Bayesian predictive intervals match the upper bounds of Johnson et al.'s predictive intervals.

@@

```{r figEVPI, fig.cap="The expected value of perfect information (EVPI) varies among anthropogenic disturbance scenarios (see increasing, decreasing and stable scenarios in Figs 1, D.1 and D.5 respectively) and the number of years projected. When disturbance is high EVPI is low, indicating that local monitoring will not alter status assessments. Increasing the forecast horizon can either increase or decrease the EVPI as the anthropogenic disturbance trend makes outcomes more or less predictable.", cache=TRUE}
knitr::include_graphics(here::here(paste0("figs/",resultScenario,"/EVPIall.png")))
```
